Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
first paragraph of intro

\section{Tor's Usability}
{\color {red}
%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.

As the most widely used anonymity tool today, Tor is primarily known as an anonymity tool. 
For this reason, user studies on Tor have been solely about, the usability of Tor as an 
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates. 
Additionally, there were a lot of features that were untested. 
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes. We ran a small pilot study 
of five journalists. This study uncovered a number of bugs and 
stopping points which has already effected concrete change in the browser.

After our first usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management. 
%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
%emphasize how we are aiming for new research, not new test cases for debugging an interface
Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
%if there are stats on this type of thing.
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool. }

>>>>

\section{Tor's Usability}
As the most widely used anonymity tool today, Tor is primarily known as an anonymity tool. 
For this reason, user studies on Tor have been solely about, the usability of Tor as an 
anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
Since then, Tor has had a lot of updates.There have been been no published usability evaluations of
Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
5.1 and later.

{\color {red}
After our first usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management. 
%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
%emphasize how we are aiming for new research, not new test cases for debugging an interface
Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
%if there are stats on this type of thing.
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool. }
